\LARGE \bf \pyRobots{}, a toolset for robot executive control

### 2014-09-18 paper.tex
Conclusion

\subsection{Summary and main contributions}

\begin{itemize}
    \item strives to simplicity (from a user perspective)
    \item Middleware independent, real-world deployments with with ROS, GenoM, NAOqi, aseba
\end{itemize}

\subsection{Future work}

\begin{itemize}
    \item control mixing policies?
    \item control over action priorities
    \item path to more complex control tool (T-REX, etc)
    \item investigate techniques in Python's {\sc asyncio} module
\end{itemize}

>>>>

We have presented here \pyRobots{}, a novel Python library supporting
development of high-level executive controllers for robotics.

Its main features include a lightweight, unobtrusive design based on code
annotations; a pre-emptive concurrency model allowing for proper, explicit
handling of task cancellation; support for event-based programming; a flexible
robot resources locking mechanism and a built-in support for 6D pose
manipulation and transformation.

\pyRobots{} does not aim at replacing large execution control frameworks. It
proposes instead an accessible set of tools to improve upon the all-too-common
\emph{ad-hoc} scripts, while remaining middleware agnostic.

The article also reports on several experimental deployments on four different
kind of robots using a mixture of four different middlewares.

While already four years old, several possible developments would offer
interesting perspectives for this tool, including (a)~the support to suspend (and
then resume) actions (which requires defining a satisfying syntax to declare
suspend/resume behaviours within actions); (b)~mechanisms to define action
priorities; (c)~investigate recent work on Python's {\tt asynchio} mechanisms
(that provide reference implementation of co-routines in Python).

Being available as an open-source platform, documented and easy to install, we
believe that these development objectives may materialize soon, as well-defined
use-cases emerge from the library's users.
